\documentclass[12pt,a4paper]{moderncv}
\usepackage[utf8]{inputenc}
\usepackage[scale=1, top = 3cm, bottom = 3cm, left = 1.5cm, right = 1.5cm]{geometry}
\recomputelengths

\moderncvtheme[black]{classic}
\firstname{TODD}
\familyname{JORDAN}
\homepage{tnjordan.github.io/}
\social[linkedin]{toddnjordan/}
\social[github]{tnjordan}
\renewcommand{\labelitemi}{-}
\usepackage[T1]{fontenc}
\renewcommand*\familydefault{\sfdefault} 

\begin{document}
\vspace*{-4\baselineskip}
\makecvtitle
\vspace{-1.5\baselineskip}

\begin{flushright}
\textbf{\large senior data scientist \textasciitilde{} paccar} \\
\textbf{\large msc analytics} \\
\end{flushright}


As a Senior Data Scientist in Paccar’s Advanced Analytics organization, I develop and deploy AI/ML models to drive efficiency, reduce costs, and enhance business strategy. I manage and optimize pipelines, ensuring seamless data flow and scalable integration. In addition to leading technical projects, I provide mentorship to junior data scientists and guide teams in implementing advanced analytics solutions.
\\
\section{Experience}
\cventry{05/2024 -- present}{Senior Data Scientist}{Paccar}{United States - Remote}{}{}
\cventry{09/2021--05/2024}{Data Scientist}{Paccar}{}{}{}
\item \textbf{Data Science:}
\begin{itemize}
    \item Lead data scientist for Paccar Financial data science projects. Developed and deployed models for financial product rates, sale price predictions, and inventory similarity detection. Served as product manager running Jira board, sprint planning, and giving executive stakeholder update presentations.
    \item Led a data science and MLOps best practices workshop in the Netherlands for DAF, delivering technical presentations and guiding a team in root cause analysis of component failures. Developed a model to predict failure risk of each truck based on historical operating conditions, facilitating an optimized recall prioritization. 
    \item Designed and led workshops on end-to-end ML pipelines, covering GCP, Snowflake, model development, API deployment with FastAPI, Docker, and CloudRun, as well as CICD with GitHub Actions, git tagging, and DVC.
    \item Conducted drivetrain reliability analysis using Cox Proportional Hazards and Weibull distributions, developing Monte Carlo simulations to estimate business liabilities.
\end{itemize}
\item \textbf{Machine Learning Operations:}
\begin{itemize}
    \item Developed CICD pipelines in GitHub Actions for scheduled model retraining, containerized deployment, and automated model promotion.
    \item Designed and implemented FastAPI services for model inference, deployed via Docker containers to GCP and AWS.
    \item Provided architectural reviews for contractor-led ML deployments, including Kafka-streaming based warranty inference systems and VertexAI based pricing products.
    \item Established logging pipelines from API logs in GCP to Snowflake for performance monitoring via Tableau dashboards.
    \item Trained MLops Engineers on team deployment standards and continued advising on new implementations.
\end{itemize}
\item \textbf{Leadership and Mentorship:}
\begin{itemize}
    \item Reviewed code and work from junior team members, setting development and coding standards.
    \item Led weekly data science team discussions and debugging sessions.
    \item GitHub administrator for Paccar's advanced analytics organization.
    \item Organized and led annual data science workshops for the analytics team.
    \item Won the 2022 and 2023 department hackathons, developing Kafka data-streaming solutions and a data enhancement pipeline to standardize truck build data for archiving.
    \item Developed and ran annual data science workshop for Paccar's advanced analytic team.
\end{itemize}


\section{Education}
\cventry{05/2024}{Master of Science in Analytics}{Georgia Tech}{}{}{
\begin{itemize}
    \item Machine Learning, Simulation, Data and Visual Analytics, Business Data Analytics, Introduction to Modelling, Introduction to Computing, High Dimensional Data, Regression Analysis
\end{itemize} 
}
\cventry{05/2013}{Master of Science in Mechanical Engineering}{North Carolina State University}{}{}{}{}
\cventry{05/2011}{Bachelor of Science in Aerospace Engineering}{North Carolina State University}{}{}{}{}

\section{Skills}
\cvitem{Programming:}{Python, SQL, Bash, Git, VBA, Java, Matlab, Fortran, R }
\cvitem{Data Science:}{Machine Learning, Natural Language Processing, LLMs, Generative AI, Deep Learning, Big Data Analytics, Time Series Analysis, Simulation, Bayesian Statistics, Regression, Computer Vision, Business Analytics, Tableau}
\cvitem{MLOps:}{GitHub Actions, Docker, GCP, FastAPI, Linux/WSL2, DVC, AWS}
\cvitem{Collaboration:}{Ideation and Project Development, Jira, Agile, Scrum, Software Testing, Product Management, Code Reviews, Pair Programming, Knowledge Transfer, Technical Presentations}



\section{Other Careers}
\cventry{06/2018--09/2021}{Patent Examiner}{United States Patent Office}{United States - Remote}{}{
\begin{itemize}
    \item Reviewed and processed patent applications, ensuring compliance with federal laws and patent office standards.
    \item Examined patents related to gas turbines and combined cycle power plants, specializing in combustion systems and their controls.
    \item Provided technical expertise in aerospace and mechanical engineering fields to evaluate the novelty of patent claims.
\end{itemize}
}
\cventry{12/2015--10/2017}{Operations Consultant}{Chodort Training Center}{Zambia}{}{
\begin{itemize}
    \item Designed and managed the construction of an off-grid solar kiln for sustainable production.
    \item Developed Excel-based management tools using Visual Basic for pricing, financial projections, and employee scheduling.
    \item Set up and managed a multi-business accounting system in QuickBooks.
    \item Led a lean manufacturing workshop to improve production quality and reduce cycle time.
\end{itemize}
}
\cventry{01/2014--12/2014}{Teacher}{Macha Central Basic School}{Zambia}{}{
\begin{itemize}
    \item Developed lesson plans and instructed a class of 55 students in Math and Science.
    \item Started a computer club for students after refurbishing previously donated Linux desktops.
    \item Conducted computer skills workshops for teachers and community members.
\end{itemize}
}
\end{document}
