\documentclass[12pt,a4paper]{moderncv}
\usepackage[utf8]{inputenc}
\usepackage[scale=1, top = 4cm, bottom = 3cm, left = 1.5cm, right = 1.5cm]{geometry}
\recomputelengths

\moderncvtheme[black]{classic}
\firstname{TODD}
\familyname{JORDAN}
\homepage{tnjordan.github.io/}
\social[linkedin]{connect-todd/}
\social[github]{tnjordan}
\renewcommand{\labelitemi}{-}
\usepackage[T1]{fontenc}
\renewcommand*\familydefault{\sfdefault} 

\begin{document}

\vspace*{-4\baselineskip}
\makecvtitle
\vspace{-1.5\baselineskip}

\begin{flushright}
\textbf{\large senior data scientist \textasciitilde{} paccar} \\
\textbf{\large msc analytics, msc mechanical engineering, bsc aerospace engineering} \\
\end{flushright}

An engineering data scientist, driven by curiosity and a passion for improving systems through efficiency gains.
I am a senior data scientist with several years of experience analyzing data, developing machine learning models, and developing and deploying CICD pipelines.  
My area of interest and expertise is at the intersection between programming and driving business value.
I have a Master's in Analytics from Georgia Tech and a Master's in Mechanical Engineering with a Bachelor's in Aerospace Engineering from NC State.

\section{Skills}
\cvitem{Programming:}{Python, SQL, Bash, Git, VBA, Java, Matlab, Fortran, R }
\cvitem{Data Science:}{Machine Learning, Natural Language Processing, LLMs, Generative AI, Deep Learning, Big Data Analytics, Time Series Analysis, Simulation, Bayesian Statistics, Regression, Computer Vision, Business Analytics, Tableau}
\cvitem{Machine Learning Operations:}{GitHub Actions, Docker, GCP, FastAPI, Linux/WSL2, DVC, AWS}
\cvitem{Collaboration:}{Ideation and Project Development, Jira, Agile, Scrum, Software Testing, Product Management, Code Reviews, Pair Programming, Knowledge Transfer, Technical Presentations}

\section{Education}
\cventry{05/2024}{Master of Science in Analytics}{Georgia Tech}{
\begin{itemize}
    \item Machine Learning, Simulation, Data and Visual Analytics, Business Data Analytics, Introduction to Modelling, Introduction to Computing, High Dimensional Data, Regression Analysis
\end{itemize} 
}
\cventry{05/2013}{Master of Science in Mechanical Engineering}{North Carolina State University}{
}
\cventry{05/2011}{Bachelor of Science in Aerospace Engineering}{North Carolina State University}{
}
\clearpage
\section{Experience}
\cventry{05/2024--present}{Senior Data Scientist}{Paccar}{United States - Remote}{}{}
\cventry{09/2021--05/2024}{Data Scientist}{}{
Senior data scientist in Paccar's advanced analytics organization, with a proven track record of developing and deploying AI/ML-enabled models, managing data pipelines, and leading technical teams. I provide leadership as the lead data scientist on each project and by mentoring junior data scientists. By continually exploring the data for business insights, I am successful at identifying trends, anomalies, and opportunities to optimize decision-making. By leveraging advanced analytics and machine learning techniques, I uncover actionable insights that drive efficiency, reduce costs, and enhance overall business strategy. Whether refining predictive models, improving data pipelines, or collaborating with stakeholders, my focus remains on transforming raw data into meaningful, high-impact solutions.
\begin{itemize}
    \item \textbf{Data Science:}
    \begin{itemize}
        \item Lead data scientist for Paccar Financial data science projects. Developed and deployed models for financial product rates, sale price predictions, and inventory similarity detection. Managed Jira board, sprint planning, and executive stakeholder presentations.
        \item Led a data science and MLOps best practices workshop in the Netherlands for DAF, delivering technical presentations and guiding a team in root cause analysis of component failures.
        \item Designed and led workshops on end-to-end ML pipelines, covering GCP, Snowflake, model development, API deployment with FastAPI, Docker, and CloudRun, as well as CICD with GitHub Actions, git tagging, and DVC.
        \item Conducted drivetrain reliability analysis using Cox Proportional Hazards and Weibull distributions, developing Monte Carlo simulations to estimate business liabilities.
    \end{itemize}
    
    \item \textbf{Machine Learning Operations:}
    \begin{itemize}
        \item Developed CICD pipelines in GitHub Actions for scheduled model retraining, containerized deployment, and automated model promotion.
        \item Designed and implemented FastAPI services for model inference, deployed via Docker to GCP and AWS.
        \item Provided architectural reviews for contractor-led ML deployments, including Kafka-streaming-based warranty inference systems and VertexAI-based pricing products.
        \item Established logging pipelines from API logs in GCP to Snowflake for performance monitoring via Tableau dashboards.
        \item Trained MLops Engineers on team deployment standards and continued advising on new implementations.
    \end{itemize}

    \item \textbf{Leadership and Mentorship:}
    \begin{itemize}
        \item Reviewed code and work from junior team members, setting development and coding standards.
        \item Led weekly data science team discussions and debugging sessions.
        \item GitHub administrator for Paccar's advanced analytics organization.
        \item Organized and led annual data science workshops for the analytics team.
        \item Won the 2022 and 2023 department hackathons, developing data-streaming solutions and Kafka-based enhancements to truck build data archiving.
        \item Develop and run annual data science workshop for Paccar's advanced analytic team.
    \end{itemize}
\end{itemize}
}

\section{Other Careers}
\cventry{06/2018--09/2021}{Patent Examiner}{United States Patent Office}{United States - Remote}{}{}{
\begin{itemize}
    \item Reviewed and processed patent applications, ensuring compliance with federal laws and patent office standards.
    \item Examined patents related to gas turbines and combined cycle power plants, specializing in combustion systems and their controls.
    \item Provided technical expertise in aerospace and mechanical engineering fields to evaluate the novelty of patent claims.
\end{itemize}
}

\cventry{12/2015--10/2017}{Operations Consultant}{Chodort Training Center}{Zambia}{}{}{
\begin{itemize}
    \item Designed and managed the construction of an off-grid solar kiln for sustainable production.
    \item Developed Excel-based management tools using Visual Basic for pricing, financial projections, and employee scheduling.
    \item Set up and managed a multi-business accounting system in QuickBooks.
    \item Led a lean manufacturing workshop to improve production quality and reduce cycle time.
\end{itemize}
}

\cventry{01/2014--12/2014}{Teacher}{Macha Central Basic School}{Zambia}{}{}{
\begin{itemize}
    \item Developed lesson plans and instructed a class of 55 students in Math and Science.
    \item Started a computer club for students after refurbishing previously donated Linux desktops.
    \item Conducted computer skills workshops for teachers and community members.
\end{itemize}
}

\cventry{09/2013--12/2013}{Avionics and Software Verification}{HCL America}{}{}{
\begin{itemize}
    \item Performed and documented manual/automated software testing on aircraft fire suppression systems.
    \item Ensured compliance with FAA regulations for software considerations in airborne systems.
\end{itemize}
}

\subsection{Internships}
\cventry{05/2012--12/2012}{Assembly Layout \& Tooling}{GE Aviation}{}{}{
\begin{itemize}
    \item Designed assembly layouts for GEnx engine workstations, doubling production capacity and improving ergonomics.
    \item Led lean manufacturing initiatives to reduce cycle time and improve continuous flow.
    \item Developed innovative tooling and part kitting solutions, saving over \$30K annually.
\end{itemize}
}

\cventry{05/2011--08/2011}{Manufacturing Standardization}{GE Aviation}{}{}{
\begin{itemize}
    \item Standardized manufacturing processes for high-volume jet engine components on mill, lathe, and CNC machines.
\end{itemize}
}

\cventry{05/2010--08/2010}{Engineered Products Group}{ILC Dover}{}{}{
\begin{itemize}
    \item Designed and drafted custom tooling for soft goods engineering programs.
    \item Provided engineering support and performed quality control checks on the aerostat manufacturing floor.
\end{itemize}
}

\cventry{05/2008--08/2008, 01/2009--05/2009, 08/2009--12/2009}{HVAC Designer}{Crenshaw Consulting}{}{}{
\begin{itemize}
    \item Designed over 50 industrial and commercial HVAC systems, ensuring compliance with building codes and regulations.
\end{itemize}
}

\end{document}